---
name: Ana Bravo
#surname: 
position: "Biostatistician | Data Scientist I"
address: "University of Miami, Miller School of Medicine"
#phone: +1 22 3333 4444
# www: 
orcid: 0009-0001-0199-3695
email: "axb3199@miami.edu"
#twitter: 
github: anbrav0
aboutme: Specialized in cleaning, modeling, and visualizing data using advanced programming languages such as R, SAS, and STATA.  
linkedin: anabravobiostats
headcolor: 414141
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    page_total: true
    keep_tex: true
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(vitae)
library(tidyverse)
library(readxl)
library(here)
library(kableExtra)
```


```{r function}
# install.packages("readxl") uncomment this if you need to install the package

readExcelSheets <- function(filename){
  # read all sheets in .xlsx 
  all <- readxl::excel_sheets(filename)
  
  # import each sheet into a list using readxl::read_excel
  list <- lapply(all, function(x) readxl::read_excel(filename, sheet = x))
  
  # save sheet name for each sheet (list)
  names(list) <- all
  
  # breaks up list and creates a dataframe for each sheet with df names matching sheet names
  list2env(list, envir = .GlobalEnv)
  

}
```


```{r load-excel, include=FALSE}
filename <- here::here("ana_bravo_vitae_cv", 
                       "Bravo_vitae_data.xlsx")

readExcelSheets(filename)

#readExcelSheets(here::here("Bravo_vitae_data.xlsx"))
```


# Education

```{r}


education %>% 
  detailed_entries( what = degree,
                    when = year,
                    with = institution,
                    where = where,
                    why = details,
                    .protect = FALSE
    
  )
```

# Research Experience 

```{r}

research |>  
  detailed_entries(
    what = role,
    when = dates,
    with = institution,
    where = where,
    why = details,
    .protect = FALSE
  )

```



# Professional Experience 


```{r professional-experience-table, include=FALSE, results='asis'}

Professional_experience <- tribble(
  ~title, ~department, ~startMonth, ~startYear, ~endMonth, ~endYear, ~where, ~details,
  
  "Lab Instructor",
  "Mathematics Department",
  "Feb",
  2019,
  "Oct",
  2020,
  "Miami Dade College",
  "Serve as a role model to motivate students to achieve their academic needs. 
  \\begin{itemize}
     \\item Advisement service.
     \\item SMART Plan creation.
     \\item Advising appointments.
     \\item Meeting with students on repeated attempts.
     \\item Assist with enrollment. 
     \\item Create, review, and modify student academic progress (MAP) for newly enrolled, transfer and transient students. 
     \\item Assist students with academic planners such as major changes and pre-requsite requirements. 
     \\item Participate in recruitment services such as orientation for First time in College (FTIC) students 
     \\item Advice and guide students who were on academic probation to implement alternative courses of action to achieve graduation. 
  \\end{itemize}",
  
  "Mathematics Tutor", 
  "Mathematics Department",
  "Oct",
  2016, 
  "Jan",
  2019, 
  "Miami Dade College",
  "Provide homework help, assist in the creation of study plans, and develop an in-depth knowledge in College Mathematics.
  \\begin{itemize}
     \\item Attend instructor meetings or requires yearly training for online courses.
     \\item Grade and score day one diagnostics exam to identify students current mathematics background
     \\item Help in the Navigation of online modalities for students such as ALEKS, myMathLab, and BlackBoard
     \\item Create study plan for students identified as at risk based on students day one diagnostics exam. 
     \\item Monitor online BlackBoard Retention Center and communicate weekly with professor.
     \\item Conduct Mastery sessions (e.g., review sessions) during tutoring service hours in preparation for exam week.
  \\end{itemize}"
  )

```


```{r profession-experience, results='asis'}
Professional_experience %>% 
  detailed_entries(
    with = title,
    what = department,
    why = details,
    when = glue::glue("{startMonth} {startYear} - {endMonth} {endYear}", .na = ""),
    where = where,
    .protect = FALSE
  )

```

# Language Skills 


```{=tex}
\begin{cvskills}  
\cvskill    {Software}    {Microsoft Office, SPSS}      
\cvskill    {Programming Languages}    {R, SAS, STATA, Python, Julia} 
\cvskill    {Reproducible Report}    {Shiny, Quarto, Markdown/Rmarkdown, LaTeX} \cvskill    {Project Management}    {REDCap}
\cvskill    {Version Control}    {Git, GitHub}
\cvskill    {Web Development}    {HTML, CSS, GitHub Pages}
\cvskill    {Languages}    {Spanish, English}
\cvskill    {Operating Systems}    {Windows, MacOS, Linux}
\end{cvskills}
```

# Presentations

```{r}

bibliography_entries("bib/presentations.bib") |> 
  arrange(desc(issued)) 

```


# Leadership, Service & Community Engagement  

```{r community-tribble, include=FALSE}

community_tribble <- tribble(
  ~title, ~department, ~startMonth, ~startYear, ~endMonth, ~endYear, ~where, ~details,
  
  "Advisor, Board of Directors: PLUMY",
  "Protecting LGBTQ+ Underserved Miami-Dade Youth",
  "Apr",
  2023,
  "Apr",
  2025, 
  "Miami-Dade County",
  "Director
  \\begin{itemize}
    \\item Board of Directors in nonprofit 501(c)(3) organization tasked to provide resources across      Miami-Dade County for unserved LGBT+ youth.
    \\item Assist in diversity, equity, and inclusion (DEI) informed decision making for non-profit      goals.
   \\end{itemize}",
  
  "Rentetion Data Core - ABCD Student Rention Workgroup",
  "ABCD Study",
  "Apr",
  2023,
  "Apr",
  2024, 
  "ABCD Study Consortium",
  "Retention Core Member
  \\begin{itemize}
    \\item Assist in the creation of retention efforts ABCD model for at risk participants.
    \\item Create, clean, and model passive withdraw participatants as well as identify participants at risk of study withdrawl.
   \\end{itemize}",
  
  "Dean Student Advisory Biostatistics Respresentative",
  "Robert Stempel College of Public Health and Social Work",
  "Aug",
  2022,
  "Aug",
  2023, 
  "Office of Student and Alumni Affairs",
  "Advisor Council Board Memeber
  \\begin{itemize}
    \\item Biostatistics Department representative, make recommendation for improvement of departmental needs.
    \\item Provide knoweldge for key decision making in Biostatistics department.
  \\end{itemize}",
  
  
  "Data Science Conference 2022",
  "DSC US Health 22",
  "Oct",
  2022,
  "Oct",
  2022,
  "FIU Kovens Conference Center",
  "Data Science Conference Logistics Volunteer
  \\begin{itemize}
    \\item Assist with logist front desk task such as check in, organization of materials.
    \\item Advise DSC attendees location of important events.
  \\end{itemize}",
  
  
  "ABCD Study Substance Use Workgroup Member",
  "ABCD Study",
  "Jun",
  2021,
  "Apr",
  2023,
  "ABCD Consortium",
  " Senior Research Assistant
  \\begin{itemize}
    \\item Provide localized insight on the RA groudfloor for the ABCD Study.
    \\item Provide assistance in reformatting script language for the ABCD Semi-structured TLFB interview.
  \\end{itemize}"
 
)

```


```{r community-engagement}
community_tribble %>% 
  detailed_entries(
    with = title,
    what = department,
    why = details,
    when = glue::glue("{startMonth} {startYear} - {endMonth} {endYear}", .na = ""),
    where = where,
    .protect = FALSE
  )
```

# Professional Membership 

```{r memberships}

membership <- tribble(
  ~title, ~member, ~startYear, ~endYear, 
  "American Public Health Association", "Member", 2022, "2024",
  "Florida Public Health Association", "Member", 2022, "Present",
  "International Network for Social Network Analysis", "Member", 2024, "Present"
)

```


```{r memberships_table}
membership%>%
  detailed_entries(
    with = title,
    what = member,
    when = glue::glue("{startYear} - {endYear}",.na = ""),
    .protect = F
  )
```

# Publications

```{r include=FALSE}
library(dplyr)
knitr::write_bib(c("vitae", "tibble"), "packages.bib")

bibliography_entries("packages.bib") %>%
  arrange(desc(author$family), issued)
```



1. Patria, R., **Bravo, A.,** Wang, W., Colon-Burgos, J.F., Ravelo, G., Castillo, B., Fizer Robinson, M., De La Rosa M., Behar-Zusman,  V. (Submitted) Higher Parental Respect is Associated with Lower Acculturation Stress Among Latino Adolescents

2. Yeguez, C.E., **Bravo, A.,** Troya, S., Pettit, J.W., (In preparation). Are Individuals with ADHD at Risk for Suicide? A Systematic Review of Longitudinal Studies. 



