%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,a4paper,]{awesome-cv}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Ana Bravo}{}

\position{Data Scientist I}
\address{University of Miami, Miller School of Medicine}

\email{\href{mailto:axb3199@miami.edu}{\nolinkurl{axb3199@miami.edu}}}
\orcid{0009-0001-0199-3695}
\github{anbrav0}
\linkedin{anabravobiostats}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}

\quote{Specialized in cleaning, modeling, and visualizing data using
advanced programming languages such as R, SAS, and STATA.}

\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{2em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\honortitlestyle{#1}}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\honordatestyle{#1}}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {December 2023}
    {Ana Bravo~~~·~~~Curriculum Vitae}
  {\thepage~ of \pageref{LastPage}~}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cventries}
    \cventry{MPH - Biostatistics}{Florida International University}{Florida, USA}{2023}{}\vspace{-4.0mm}
    \cventry{BA - Psychology}{Florida International University}{Florida, USA}{2018}{}\vspace{-4.0mm}
    \cventry{AA - Psychology}{Miami Dade College}{Florida, USA}{2016}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{research-experience}{%
\section{Research Experience}\label{research-experience}}

\begin{cventries}
    \cventry{Data Scientist I, Primary Investigator: Mariano Kanamori, Ph.D.}{University of Miami Miller School of Medicine}{Department of Public Health}{Aug 2023 - Present}{\begin{cvitems}
\item Utilize R for data wrangling, manipulation, cleaning, statistical analysis, and visualizations to extract insight from social network data.
\item Develop and deploy custom R scripts and functions to automate data import, summarization, and transformation to streamline processes.
\item Skilled in visualizing ego-centric (personal network) data using a variaty of different R packages such as {egoR}, {igraph}, and {SNA} to analyze different patterns of communication within a network.
\item Skilled in creating dynamic and static reproducible reports using Quarto and Shiny to create informative visualizations to show survey respond trends in Likert scale data.
\item Utilize ggplot2, ggstatplot, and Plotly to create health-related visualizations on Pre-exposure prophylaxis (PrEP) use among a Latino sample in South Florida.
\item Proficient in Tidygraph principles such as adding graphs, edge, and centrality measures to provide tidy API for network manipulation.
\end{cvitems}}
    \cventry{Data Analyst Intern, Primary Supervisors: Weize Wang, MPH and Patria Rojas, Ph.D., MPH, MSW}{Center for Research on U.S. Latino HIV/AIDS and Drug Abuse}{Florida International University}{Dec 2022 - Jun 2023}{\begin{cvitems}
\item Analytical skills and proficiency in SAS, STATA, SQL and R Programming language to analyze longitudinal, repeated measures, and cohort data.
\item Performs various data analytics manipulation tools such as cleaning, transforming, pivoting and visualizing data for optimal data use.
\item Performed statistical analysis using a variety of statistical models such as parametric, non-parametric hypothesis testing, linear regression, logistic regression, survival analysis, and longitudinal data modeling using GEE and mixed effects model methods.
\item Experienced in cleaning and merging big  data using pivotting techniques in R, SAS, and SQL.
\item Skilled in using a wide variety of data analytical methodologies to address issues such as data missingness and trouble shooting technical difficulties.
\item Interpreted data analysis results to investigators with and without statistical subject matter knowledge
\end{cvitems}}
    \cventry{Senior Research Assistant, Primary Investigator: Raul Gonzalez, Ph.D.}{Substance Use Neuropsychology Lab}{Florida International University}{Feb 2020 - Jul 2023}{\begin{cvitems}
\item Conduct assessment for the longitudinal Adolescent Brain Cognitive Development (ABCD) Study under the direct supervision of Dr. Raul Gonzalez.
\item Administer clinical interviews (e.g., KSADS, PPS, Substance use questionnaires, Alcohol, Nicotine and Marijuana TLFB measurements to school aged children for a ten-year longitudinal study.
\item Administer and score neuropsychological and neuro-behavioral tasks (RAVL-T, NIH Tool Box, Emotional Stroop Task) with ABCD participants.
\item Conduct suicide-risk assessment under the supervision of an onsite clinician during protocol visits and conduct suicidality follow up with parents.
\item Conduct Time Line Follow Back Interview (TLFB) to obtain youth estimates of past year marijuana, cigarette and other substance use.
\item Collection of different biological specimen samples from a variety of different domains such as hair, urine, saliva, blood, DNA saliva sample, and Drager breathalyzer.
\end{cvitems}}
    \cventry{Research Assistant, Primary Investigator: Jeremy Pettit, Ph.D.}{Child Anxiety and Phobia Program}{Florida International University}{Apr 2017 - Feb 2020}{\begin{cvitems}
\item Assisted during the administration of evidence based asessment e.g., exposure therapy and treatment to chldren and adolescents with anxiety and depression threshhold and sub-threshold disorders.
\item Organization of clinical case files for youth and adolescents that come into phobia center for anxiety and depression treatment.
\item Conduct intake phone interviews on potential participants to determine treatment plan for anxitey and depressive disorders (GAD, MDD, SAD etc.)
\item Assisted in the completion of psychosocial questionnaires during clinical interview as well as administer computer based tasks such as Flanket test for executive functions.
\item Participated in data capture for diagnostic code of children and parents with anxiety dirsorder that meet criteria for DSM-5 related disorders for different time points (pre, post, and follow-up.)
\item Assist, recruit, and schedule participansts for incoming projects such as Attention Training (AT-RCT) for social anxiety study that included EEG assessment for participants.
\end{cvitems}}
    \cventry{Research Assistant, Primary Investigator: Erica D. Musser, Ph.D.}{Assess Behavior, Cognition, and Emotion Regulation in Children and Adolescents Lab}{Florida International University}{May 2017 - May 2019}{\begin{cvitems}
\item Participate in FIU's Summer Treatment Program (STP) in collboration with ABCDERICA Lab to collect physiological data (e.g., heart rate electrodermal activity) from school ages children with ADHD and comorbid disorders.
\item Set up Mindware/BioLab electrodes on youth during assessment of ADHD and Emo meds protocol
\item Run and conduct ADHD protocol task such as: resting baseline, neutral picture assessment, COIN, BARTLG to compare control vs. ADHD diagnosis group.
\item Perform video transcripts of youth during Emotional and Parenting in Childhood (EPIC) Study conducted by Rachel Tenenbaum, Doctoral student.
\item Conduct data cleaning procedures on heart rate variability (HRV) cardiac impedance (IMP) and electrodermal activity (EDA) measurements on Mindware software using participant data.
\end{cvitems}}
\end{cventries}

\hypertarget{professional-experience}{%
\section{Professional Experience}\label{professional-experience}}

\begin{cventries}
    \cventry{Mathematics Department}{Lab Instructor}{Miami Dade College}{Feb 2019 - Oct 2020}{\begin{cvitems}
\item Serve as a role model to motivate students to achieve their academic needs. 
  \begin{itemize}
     \item Advisement service.
     \item SMART Plan creation.
     \item Advising appointments.
     \item Meeting with students on repeated attempts.
     \item Assist with enrollment. 
     \item Create, review, and modify student academic progress (MAP) for newly enrolled, transfer and transient students. 
     \item Assist students with academic planners such as major changes and pre-requsite requirements. 
     \item Participate in recruitment services such as orientation for First time in College (FTIC) students 
     \item Advice and guide students who were on academic probation to implement alternative courses of action to achieve graduation. 
  \end{itemize}
\end{cvitems}}
    \cventry{Mathematics Department}{Mathematics Tutor}{Miami Dade College}{Oct 2016 - Jan 2019}{\begin{cvitems}
\item Provide homework help, assist in the creation of study plans, and develop an in-depth knowledge in College Mathematics.
  \begin{itemize}
     \item Attend instructor meetings or requires yearly training for online courses.
     \item Grade and score day one diagnostics exam to identify students current mathematics background
     \item Help in the Navigation of online modalities for students such as ALEKS, myMathLab, and BlackBoard
     \item Create study plan for students identified as at risk based on students day one diagnostics exam. 
     \item Monitor online BlackBoard Retention Center and communicate weekly with professor.
     \item Conduct Mastery sessions (e.g., review sessions) during tutoring service hours in preparation for exam week.
  \end{itemize}
\end{cvitems}}
\end{cventries}

\hypertarget{language-skills}{%
\section{Language Skills}\label{language-skills}}

\begin{table}[!h]
\centering
\begin{tabular}{ll>{\raggedright\arraybackslash}p{27em}}
\toprule
Programming & Software & Description\\
\midrule
R & Github & CV automation, Github.io hosted website, cleaning, visualizing data.\\
Rstudio & COVID-19 Project & COVID-19 projected South Florida infection and vaccination rate.\\
Quarto/Rmarkdown & LateX & Ouput html, pdf, and word, documents using Rmarkdown.\\
SAS & SAS 9.4 & Graduate project interested in looking at 2019 YRBSS Marijuana, cigarette, and vaping use among highschool aged students.\\
STATA & STATA MP17 Citrix & Regression models, correlation matrix, pre-post analysis, Cox PH models.\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{presentations}{%
\section{Presentations}\label{presentations}}

\hypertarget{bibliography}{}
\leavevmode\vadjust pre{\hypertarget{ref-apha1}{}}%
\CSLLeftMargin{1. }%
\CSLRightInline{Bravo, A., Wang, W., Colon-Burgos, J., Gomez-Estern, B.,
Behar-Zusman, V., \& Rojas, P. (2023). \emph{Examining sociocultural
factors of hispanic stress: A community based remote study among latino
adolescents in south florida}. Florida International University,
University of Miami; American Public Health Association 2023 Annual
Meeting and Expo.}

\leavevmode\vadjust pre{\hypertarget{ref-apha2}{}}%
\CSLLeftMargin{2. }%
\CSLRightInline{Rojas, P., Wang, W., Novoa, O., Colon-Burgos, J.,
Ravelo, G. J., Sanchez, M., Cano, M. A., Khalona, M., Bravo, A., De La
Rosa, M., \& Behar-Zusman, V. (2023). \emph{A remote intervention on HIV
and substance use during the COVID-19 pandemic: A community based
participatory randomized clinical trial targetting adult latino men in
south florida}. Florida International University, University of Miami;
American Public Health Association 2023 Annual Meeting and Expo.}

\hypertarget{leadership-service-community-engagement}{%
\section{Leadership, Service \& Community
Engagement}\label{leadership-service-community-engagement}}

\begin{cventries}
    \cventry{Protecting LGBTQ+ Underserved Miami-Dade Youth}{Advisor, Board of Directors: PLUMY}{Miami-Dade County}{Apr 2023 - Apr 2025}{\begin{cvitems}
\item Directors
  \begin{itemize}
    \item Board of Directors in nonprofit 501(c)(3) organization tasked to provide resources across      Miami-Dade County for unserved LGBT+ youth.
    \item Assist in diversity, equity, and inclusion (DEI) informed decision making for non-profit      goals.
   \end{itemize}
\end{cvitems}}
    \cventry{ABCD Study}{Rentetion Data Core - ABCD Student Rention Workgroup}{ABCD Study Consortium}{Apr 2023 - Apr 2024}{\begin{cvitems}
\item Retention Core Member
  \begin{itemize}
    \item Assist in the creation of retention efforts ABCD model for at risk participants.
    \item Create, clean, and model passive withdraw participatants as well as identify participants at risk of study withdrawl.
   \end{itemize}
\end{cvitems}}
    \cventry{Robert Stempel College of Public Health and Social Work}{Dean Student Advisory Biostatistics Respresentative}{Office of Student and Alumni Affairs}{Aug 2022 - Aug 2023}{\begin{cvitems}
\item Advisor Council Board Memeber
  \begin{itemize}
    \item Biostatistics Department representative, make recommendation for improvement of departmental needs.
    \item Provide knoweldge for key decision making in Biostatistics department.
  \end{itemize}
\end{cvitems}}
    \cventry{DSC US Health 22}{Data Science Conference 2022 Volunteer}{FIU Kovens Conference Center}{Oct 2022 - Oct 2022}{\begin{cvitems}
\item Data Science conference Volunteer
  \begin{itemize}
    \item Assist with logist front desk task such as check in, organization of materials.
    \item Advise DSC attendees location of important events.
  \end{itemize}
\end{cvitems}}
    \cventry{ABCD Study}{ABCD Study Substance Use Workgroup Member}{ABCD Consortium}{Jun 2021 - Apr 2023}{\begin{cvitems}
\item Research Assistant trainee input
  \begin{itemize}
    \item Provide localized insight on the RA groudfloor for the ABCD Study.
    \item Provide assistance in reformatting script language for the ABCD Semi-structured TLFB interview.
  \end{itemize}
\end{cvitems}}
    \cventry{Child Anxiety and Phobia Lab}{The Childrens Trust Expo Recruitment}{MDC Wolfson Campus}{Sept 2018 - Sept 2018}{\begin{cvitems}
\item Recruitor for EMU study and Child Anxiety and Phobia Program.
  \begin{itemize}
    \item Offer resources to families to participate in sleep study and anxiety and treatment services at FIU.
    \item Recruit for EMU study, a sleep study interested in looking at sleep and anxiety using MRI facilities.
  \end{itemize}
\end{cvitems}}
    \cventry{Child Anxiety and Phobia Lab}{Open House and Parent Resource provider}{Miami Heights Elementary}{Sept 2019 - Sept 2019}{\begin{cvitems}
\item Outreach Program Efforts.
  \begin{itemize}
    \item Parent resource night outreach program to school age children and parents interested in treatment services.
    \item Offer CCF resources to parents available in the South Florida Area.
  \end{itemize}
\end{cvitems}}
\end{cventries}

\hypertarget{professional-membership}{%
\section{Professional Membership}\label{professional-membership}}

\begin{cventries}
    \cventry{Member}{American Public Health Association}{}{2022 - Present}{}\vspace{-4.0mm}
    \cventry{Member}{Florida Public Health Association}{}{2022 - Present}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{publications}{%
\section{Publications}\label{publications}}

Yeguez, C.E., \textbf{Bravo, A.,} Troya, S., Pettit, J.W., (In
preparation). Are Individuals with ADHD at Risk for Suicide? A
Systematic Review of Longitudinal Studies.

\textbf{Bravo, A.,} Wang, W., Rojas, P., (In preparation). Examining
Sociocultural Factors of Hispanic Stress: A Community Based Repeated
Measures Study in South Florida among Latinx Adolescents.


\label{LastPage}~
\end{document}
